\thetitle

### 2020-11-14 writing/related.tex
fix basic latex mistakes in rudimentary way
draft of benchamrks and mutators
adding related work

\begin{itemize}
  \item  GT: systems we don't represent
  \item Mutation testing
  \itme Fault localization
\end{itemize}

>>>>

This paper builds on~\citet{lksfd-popl-2020}'s one-of-a-kind analysis of
blame for higher-order contracts. They do not spell out the notion of the
rational programmer but the basic ingredients of our technique derive
directly from theirs. Specifically, we adapt their empirical technique to
gradual typing which requires the development of custom
mutators, careful selection of debugging scenarios and generalization of
the technique to allow the comparison of different semantics.

Besides the three semantics we consider, the literature on gradual typing
comes with a plethora of different approaches. For example, Pyret
(\shorturl{https://www.}{pyret.org}) treats function types same as Natural
and data types same as Erasure. The Forgetful~\cite{cl-icfp-2017} and the
Amnesic~\cite{gfd-oopsla-2019} semantics are similar  to Transient but
use wrappers instead of inlined checks.  Nom~\cite{mt-oopsla-2017} and
other \emph{concrete\/} semantics~\cite{wnlov-popl-2010, rsfbv-popl-2015,
mt-oopsla-2017, rzv-ecoop-2015, rat-oopsla-2017} assume that every type
maps to a unique known tag and they perform type tag checks  for every
value that crosses from typed to untyped parts of a program or vice versa.
With the exception of Amnesic~\cite{gfd-oopsla-2019}, all the above
semantics forego blame. However, Amnesic is a mere
theoretical construction and is not meant as a blueprint for an
implementation.
